---
title: "mdthemes"
output: github_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  fig.path = "man/figures/README-"
)
```

[![R build status](https://github.com/thomas-neitmann/mdthemes/workflows/R-CMD-check/badge.svg)](https://github.com/thomas-neitmann/mdthemes/actions)
[![CRAN Version](https://www.r-pkg.org/badges/version/mdthemes?color=green)](https://cran.r-project.org/package=mdthemes)
[![Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/mdthemes?color=green)](https://cran.r-project.org/package=mdthemes)
[![Lifecycle Status](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)


## Overview

`{mdthemes}` adds support for rendering text as markdown to your favorite `{ggplot2}` themes thanks to the awesome `{ggtext}` package.


## Installation

The package is available from CRAN.

```r
install.packages("mdthemes")
```

Alternatively, you can install the latest development version from GitHub.

```r
if (!requireNamespace("remotes", quietly = TRUE)) {
  install.packages("remotes")
}
remotes::install_github("thomas-neitmann/mdthemes", upgrade = "never")
```


## Usage

Currently, `{mdthemes}` contains all themes from `{ggplot2}`, `{ggthemes}`, `{hrbrthemes}`, `{tvthemes}` and `{cowplot}` with support for rendering text as markdown. All themes start with `md_` followed by the name of the original theme, e.g. `md_theme_bw()`.

```{r examples, message=FALSE, warning=FALSE, fig.show='hold', out.width='50%'}
library(ggplot2)
library(mdthemes)
data(mtcars)

p <- ggplot(mtcars, aes(hp, mpg)) +
  geom_point() +
  labs(
    title = "This is a **bold** title",
    subtitle = "And an *italics* subtitle",
    x = "**_hp_**",
    caption = "<span style = 'color:blue'>A blue caption</span>"
  )

p + theme_minimal()
p + md_theme_minimal()
```

```{r examples_cont, fig.show='hold', out.width='50%'}
p + ggthemes::theme_fivethirtyeight()
p + md_theme_fivethirtyeight()
```


## Going further

To learn more about `{mdthemes}` check out [this blog post](https://thomasadventure.blog/posts/mdthemes-is-on-cran-markdown-powered-themes-for-ggplot2/) accompanying the first CRAN release.
